\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2020-07-02 redaction/submission_JEGeo/revision/referees/answers/Answer_referee1_Lise.tex

$$\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}} = \alpha \frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} + \gamma_{i} +\gamma_{k}+\epsilon_{ik}$$

Or equivalently, taking logs:
$$\Delta \log \widetilde{p}_{ikt}= \alpha\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} +\gamma_{i} +\gamma_{k}+\epsilon_{ikt}$$

\noindent with the LHS being the growth rate of the fas price (between $t$ and $t-1$), the first term in the RHS the change in duty tax rates, the second and third terms fixed effects to capture changes in the ``firm-specific price'' $\bar{p}_{ik}$, $\epsilon_{ik}$ being the residual. Notice though that the structure of fixed effects should remain consistent between the first and the second stages. This implies to rather consider the following functional form of the first-stage equation:

\begin{equation}
\Delta \log \widetilde{p}_{ikt} = \alpha\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} +\gamma_{i} +\gamma_{s}+\epsilon_{ikt} \label{eq:firststage_Deltalog}
\end{equation}

If this reasoning is correct,
\begin{itemize}
\item we should take as predicted value only the predicted price without the fixed effects:
$$\left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV} = \widehat{\alpha}\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $$
\item and we should expect a value of the coefficient $\widehat{\alpha}$ between $\Delta \log \widetilde{p}_{ikt}$ and $\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $ between $-1$ and $0$, depending on the degree of ``pricing-to-market'' of firms.
    \begin{itemize}
    \item[-] $\alpha = 0$ corresponds to the case where the firm does not adjust its fas price to the change in tax duty, that would cancel out the influence of the tax duty change on the price paid by the US consumers; this rather corresponds to small firms which do not have enough market power to manipulate their prices following changes in international competition;
    \item[-] $\alpha <0$ corresponds to the degree of``pricing-to-market'' as the firm offsets the impact of the tax change of the price paid by the final consumer by adjusting her producer price in the opposite direction of the tax change,
    \item[-] with $\alpha = -1$ being the extreme case of ``full PTM'' where the firm fully compensates the tax duty change. As shown by Berman, Martin, Mayer (REStats 2012), this is more likely larger firms.
    \end{itemize}
\end{itemize}

Once this is done, we can rebuild the instrumented fas price in level (at time $t$):

\begin{eqnarray*}
\widetilde{p}^{IV}_{ikt} = \widetilde{p}_{ikt-1}\left[1 + \left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV}\right]
\end{eqnarray*}

with $\widehat{\widetilde{p}}_{ikt}$ the instrumented fas price at time $t$, for product $k$ from country $i$; $\widetilde{p}_{ikt-1}$ the observed lagged fas price for the same $i,k$ couple; and $ \left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV}$ the predicted growth rate of the fas price based on duty changes.

\subsection{First-stage equation in level}

Alternatively, one can run the first-stage equation in log level, consistently with the second-stage log-level specification. Further, in accordance with the referee's suggestion, this also implies including the lagged price as instrument. Starting from Equation (\ref{eq:firststage_Deltalog}), we thus run as first-stage specification:

\begin{equation}
\log \widetilde{p}_{ikt} = \alpha\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} + \beta \log\widetilde{p}_{ikt-1}  +\gamma_{i} +\gamma_{s}+\epsilon_{ikt} \label{eq:firststage_log}
\end{equation}

Consistently with the cross-section analysis adopted by now, the first-stage equation is estimated on a yearly basis (and by transport mode). We then build the instrumented fas price

\begin{eqnarray*}
&&\log \widetilde{p}_{ikt}^{IV} = \widehat{\alpha}\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} + \widehat{\beta}\log\widetilde{p}_{ikt-1} \\
\rightarrow &&\widetilde{p}_{ikt}^{IV}  = \exp^{\log \widetilde{p}_{ikt}^{IV}}
\end{eqnarray*}
